---
title: "ISLR Exercise 3.7.11"
format: pdf
editor: visual
---

In this problem, we will investigate the t-statistic for the null hypothesis $H_0 : \beta = 0$ in simple linear regression without an intercept. To begin, we generate a predictor `x` and an response `y` as follows:

```{r}
set.seed(1)
x <- rnorm(100) # picks 100 independent normally distributed samples with mean 0 and stdev 1
y <- 2*x+ rnorm(100)
```

### a) Perform a simple linear regression of `y` onto `x` without an intercept. Report the coefficient estimate $\hat{\beta}$, the standard error of this coefficient estimate, and the t-statistic and p-value associated with the null hypothesis $H_0: \beta = 0$.

```{r}
fit1 <- lm(y ~ x + 0)
summary(fit1)
```
So the coefficient estimate is 1.9939, the std error is 0.1065, the t-statistic is 18.73, the p-value is very small (<2e-16)
### b) Now perform x onto y without intercept. Do the same as above. Comment on the results and again report the values similar to above.

```{r}
fit2 <- lm(x ~ y + 0)
summary(fit2)
```
T value is the same, p value is the same, estimate is .39111, std error is 0.02089
